### 2014-07-09 tex/main-body-text.tex
some final edits to conclusion

\section*{Conclusions}
In the past decade, the use of genetic markers to identify population structure and to attempt inference of
the number of genetic clusters ($K$) in a collection has dramatically increased in the fields of ecology, evolution, epidemiology, and conservation
genetics. By virtute of this expanding desire to identify $K$ there has been a push to 
develop fast and easy-to-use methods that can accurately infer $K$. We show that {\sc flock}, a program billed as providing
``more accurate allocations and more reliable estimates of $K$ [while running]
much faster than {\sc structure} \citep[][p.~734]{Duc&Tur2012},'' may not, in fact, represent such 
a radical departure from {\sc structure} itself.  In particular, we have shown that the algorithm implemented 
in {\sc flock} is a simulated annealing algorithm for the Bayesian 
MAP estimate from a marginalized and restricted form of the {\sc structure} model.  
Given such similarities between the two methods it is not surprising that
we observed relatively
congruent results between the ``best run'' from {\sc flock} and {\sc structure} using 
a real data set from \textit{O. mykiss}.

@@

One of the major claimed advantages of {\sc flock} over other methods for genetic clustering (like {\sc structure})
is that, ``The very short processing times for each run of {\sc flock} allows for
comparing partitions from many runs of each $K$'' \citep[][p.~735]{Duc&Tur2012}.
While the authors observed faster processing times (relative to other methods) in their 
comparisons, we did not observe the same advantage in our analysis. This appears to result from two issues. First,
our example data set was an order of magnitude larger than the largest data set analyzed in \citet{Duc&Tur2012}.  Second, 
in the comparison by \citet{Duc&Tur2012}, 
{\sc flock} was set to perform 50 runs and 20 iterations for each $K$ from 1 to four more than 
the true value of $K$, and computing times for that analysis were compared to times for ten iterations of {\sc structure} using 
a 50,000 sweep burn-in followed 
by a 200,000 sweep sample from the posterior of $K$ from 1 to three more than the true 
value of $K$. 
To us it seemed reasonable to compare, for each $K$, one iteration of {\sc structure} (50,000 burn in and 200,000 sample collection sweeps)
to one iteration of {\sc flock} (50 different starting allocations that are reallocated 20 times) 
as both are used to provide a single estimate of the partition of individuals into clusters. One could
argue that it would be more appropriate to compare the running times of the programs according to the number
of opportunities that each individual's cluster membership has for random initialization and reallocation.  Under 
such a perspective, {\sc flock}'s 50 different starting allocations and 20 reallocations should be compared to
50 separate runs of structure, each of length 20 sweeps, which would surely give {\sc structure}
an apparent advantage in speed.  Regardless, while it may hold that {\sc flock}
is able to process small datasets quickly enough to compete with {\sc structure},
the rapid increase in our ability to economically
genotype a large number of individuals for a great many loci, may render this advantage less relevant to many 
study designs in the future.

>>>>

\section*{Conclusions}
In the past decade, the use of genetic markers to identify population structure and to attempt inference of
the number of genetic clusters ($K$) in a collection has dramatically increased in the fields of ecology, evolution, epidemiology, and conservation
genetics. By virtute of this expanding desire to identify $K$ there has been a push to 
develop fast and easy-to-use methods that can accurately infer $K$. We show that {\sc flock}, a program billed as providing
``more accurate allocations and more reliable estimates of $K$ [while running]
much faster than {\sc structure} \citep[][p.~734]{Duc&Tur2012},'' may not, in fact, represent such 
a radical departure from {\sc structure} itself.  In particular, we have shown that the algorithm implemented 
in {\sc flock} is a simulated annealing algorithm for the Bayesian 
MAP estimate from a marginalized and restricted form of the {\sc structure} model.  
Given such similarities between the two methods, it is not surprising that
we observed relatively
congruent results between the ``best run'' from {\sc flock} and {\sc structure} using 
a real data set from \textit{O. mykiss}.

@@

One of the major claimed advantages of {\sc flock} over other methods for genetic clustering (like {\sc structure})
is that, ``The very short processing times for each run of {\sc flock} allows for
comparing partitions from many runs of each $K$'' \citep[][p.~735]{Duc&Tur2012}.
While the authors observed faster processing times (relative to other methods) in their 
comparisons, we did not observe the same advantage in our analysis. This appears to result from two issues. First,
our example data set was an order of magnitude larger than the largest data set analyzed in \citet{Duc&Tur2012}.  Second, 
in the comparison by \citet{Duc&Tur2012}, 
{\sc flock} was set to perform 50 runs and 20 iterations for each $K$ starting at 2 and ending when 
one of the stopping conditions was met, and computing times for that analysis were compared to ten iterations of {\sc structure} using 
a 50,000 sweep burn-in followed 
by a 200,000 sweep sample from the posterior of $K$ from 1 to three more than the most likely 
value of $K$.
To us it seemed reasonable to compare, for each $K$, one iteration of {\sc structure} (50,000 burn in and 150,000 sample collection sweeps)
to one iteration of {\sc flock} (50 different starting allocations that are reallocated 20 times) 
as both are used to provide a single estimate of the partition of individuals into clusters. One could
argue that it would be more appropriate to compare the running times of the programs according to the number
of opportunities that each individual's cluster membership has for random initialization and reallocation.  Under 
such a perspective, {\sc flock}'s 50 different starting allocations and 20 reallocations should be compared to
50 separate runs of structure, each of length 20 sweeps, which would surely give {\sc structure}
an apparent advantage in speed.  Regardless, while it may hold that {\sc flock}
is able to process small datasets quickly enough to compete with {\sc structure},
the rapid increase in our ability to economically
genotype a large number of individuals for a great many loci, may render this advantage less relevant to many 
study designs in the future.
